Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Semantics: positive -> non-negative
Wording

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all positive integers.
But what about negative ones? Let's assume that we want our
implementation to throw an exception in this case. We would
specify it like this.

@@

RSpec provides an explicit mechanism to facilitate reuse of pieces of
specification.~\cite{rspec}
In Haskell we get reusability for free, it does not require any
explicit support from Hspec.

@@

This not only shows that functional programming can deliver what OO
has always claimed, but it is also awfully useful.
\end{quote}

Here is a specification that documents that a list is a monoid:

@@

\noindent And it is possible to to make this specification reusable,
by abstracting over the type:

>>>>

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all non-negative integers.
But what about negative ones? Let's assume that we want our
implementation to throw an exception in this case. We would
specify it like this.

@@

RSpec provides an explicit mechanism to facilitate reuse of pieces of
specification~\cite{rspec}.
In Haskell we get reusability for free, it does not require any
explicit support from Hspec.
The following example illustrates this.

@@

This not only shows that functional programming can deliver what OO
has always claimed, but it is also awfully useful.
\end{quote}
Here is a specification that documents that a list is a monoid:

@@

\noindent It is possible to to make this specification reusable, by
abstracting over the type:
